Peak area control doc

### 2024-03-12 targeted/targeted_control.Rmd
Manuscript as sent to coauthors

ggplot(rfrs, aes(x=Falkor, y=Mesotransect, label=compound_name)) +
  geom_point()
plotly::ggplotly()
rfrs %>%
  filter(compound_name!="Choline") %>%
  ggplot(aes(x=Falkor, y=Mesotransect, label=compound_name)) +
  geom_point() +
  geom_abline(slope = 1, intercept = 0) +
  lims(x=c(0, NA), y=c(0, NA)) +
  coord_fixed()
```

>>>>

ggplot(rfrs, aes(x=Falkor, y=Mesotransect, label=compound_name)) +
  geom_point()
plotly::ggplotly()
rfrs %>%
  filter(compound_name!="Choline") %>%
  ggplot(aes(x=Falkor, y=Mesotransect, label=compound_name)) +
  geom_point() +
  geom_abline(slope = 1, intercept = 0) +
  lims(x=c(0, NA), y=c(0, NA)) +
  coord_fixed()

rfs <- read_csv("made_data/rf_ratios.csv")
rfs %>%
  select(compound_name, cruise, rf_matrix) %>%
  pivot_wider(names_from = cruise, values_from = rf_matrix) %>%
  ggplot(aes(x=Falkor, y=Mesotransect, label=compound_name)) +
  geom_point() +
  geom_abline(slope = 1, intercept = 0) +
  lims(x=c(0, NA), y=c(0, NA)) +
  coord_fixed() +
  scale_y_log10() +
  scale_x_log10()
plotly::ggplotly()
```
